---
title: "individual2"
author: "Cody Nielsen and Matthew Eisner"
date: "9/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
str(choco)
```

We will be exploring what aspects of the chocolates may affect taste. Before setting off to the exploration, answer the following questions.

1. How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.
```{r}
hist(choco$Rating,main="Chocolate", breaks=10)
boxplot(choco$Rating)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
year <- table(choco$Date)
barplot(year, las=2, main="Ratings per Year",xlab="Year",ylab="Rating")
```

3. Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain.
```{r}
plot(choco$Rating ~ choco$Cocoa_Percent)
x <- choco[,c('Rating', 'Cocoa_Percent')]
cor(x)
```
There does not seem to be a correlation between the cocoa percent and the rating

4. 
```{r}
char1 <- table(choco$Characteristics1,choco$Rating)
barplot(char1)
head(char1, 15)
char2 <- table(choco$Characteristics2,choco$Rating)
barplot(char2)
head(char2, 15)
char3 <- table(choco$Characteristics3,choco$Rating)
barplot(char3)
head(char3, 15)
char4 <- table(choco$Characteristics4,choco$Rating)
barplot(char4)
head(char4, 15)
```
It seems that the first characteristic has more of an effect on the rating than the following characteristics.

5. 
Rating based on the origin of the bean
```{r}
cocoaLoc <- table(choco$Bean_Origin,choco$Rating)
cocoaLoc
```

```{r}
library(ggplot2)

par(mfrow=c(2,2))

DR <- choco$Rating[choco$Bean_Origin == 'Dominican Republic']
Ecu <- choco$Rating[choco$Bean_Origin == 'Ecuador']
MAD <- choco$Rating[choco$Bean_Origin == 'Madagascar']
Per <- choco$Rating[choco$Bean_Origin == 'Peru']
Ven <- choco$Rating[choco$Bean_Origin == 'Venezuela']

hist(DR, main="Dominican Republic", xlab="Rating", xlim=c(1,4), ylim=c(0,50))
abline(v=mean(DR), col="red", lwd=2)
hist(Ecu, main="Ecuador", xlab="Rating", xlim=c(1,4))
abline(v=mean(Ecu), col="red", lwd=2)
hist(MAD, main="Madagascar", xlab="Rating", xlim=c(1,4), ylim=c(0,50))
abline(v=mean(MAD), col="red", lwd=2)
hist(Per, main="Peru", xlab="Rating", xlim=c(1,4), ylim=c(0,50))
abline(v=mean(Per), col="red", lwd=2)
hist(Ven, main="Venezuela", xlab="Rating", xlim=c(1,4))
abline(v=mean(Ven), col="red", lwd=2)
country <- c('Dominican Republic', 'Ecuador', 'Madagascar', 'Peru', 'Venezuela')
mean <- c(mean(DR), mean(Ecu), mean(MAD), mean(Per), mean(Ven))
stdn <- c(sd(DR), sd(Ecu), sd(MAD), sd(Per), sd(Ven))
data <- data.frame(country, mean, stdn)
head(data)
```